\thesistitle

### 2019-08-19 sections/related_work.tex
Badri

\subsection{Effect of clone refactoring on the size of unit test cases}
\cite{badri2019measuring}
\todo{TODO}

>>>>

\subsection{Effect of clone refactoring on the size of unit test cases}
Badri et al.~\cite{badri2019measuring} measure the impact on clone refactoring on metrics that affect the testability of software. The metrics they measure are size, cyclomatic complexity and coupling. To collect this data, they used two systems that have been clone refactored. They conclude that there is a strong and positive correlation between clone refactoring and the reduction of the size of unit test cases. They also show that code quality attributes that are related to testability are significantly improved.
